Matching bullets

### 2015-11-17 imaging-paper.Rnw
lines as geom

qplot(data=subset(dbr111, x <= 100 & x >= 95), y, value, colour=factor(x)) +
  geom_line(aes(x=xpred, y=ypred, group=x), 
            colour="black", size=0.25) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom") + coord_equal()
@

@@

<<residual, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 80 & x >=75), y, value-ypred, colour=factor(x)) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom")
@

<<residual2, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 5), y, value-ypred, colour=factor(x)) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom")
@

@@

<<circlefits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlayed.', fig.pos='H'>>=
qplot(y, resid, data=subset(db2, x <= 80 & x >=75), colour=factor(x)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_point(aes(y, resid), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==1, x <= 80, x >=75)[,c("y", "resid")]) + ggtitle("Part 1 of Bullet 1 in black")
@

If we perform a similar routine for part 2 of bullet 1, we obtain the figure give in Figure \ref{fig:circlefits2}.

<<circlefits2, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Circle fit for each cross section of bullet 2, with part 2 of bullet 1 overlayed.', fig.pos='H'>>=
qplot(y, resid, data=subset(db2, x <= 80 & x >=75), colour=factor(x)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_point(aes(y, resid), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x <= 80, x >=75)[,c("y", "resid")]) + ggtitle("Part 2 of Bullet 1 in black")
@

>>>>

qplot(data=subset(dbr111, x <= 100 & x >= 95), y, value, colour=factor(x), geom="line", size=I(1)) +
  geom_line(aes(x=xpred, y=ypred, group=x), 
            colour="grey30", size=0.25) +
  scale_colour_brewer("Cross-sections at x", palette="Paired") + 
  ylab(expression(paste("Surface Measurements (in ",mu,m,")"))) + 
  theme_bw() + 
  theme(legend.position="bottom") + coord_equal()
@

@@

<<residual, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 80 & x >=75), y, value-ypred, colour=factor(x), geom="line", size=I(1)) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom")
@

<<residual2, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 5), y, value-ypred, colour=factor(x),
      geom="line", size=I(1)) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom")
@

@@

<<circlefits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlayed.', fig.pos='H'>>=
qplot(y, resid, data=subset(db2, x <= 80 & x >=75), colour=factor(x), geom="line", size=I(1)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==1, x <= 80, x >=75)[,c("y", "resid", "x")]) + ggtitle("Part 1 of Bullet 1 in black")
@

If we perform a similar routine for part 2 of bullet 1, we obtain the figure given in Figure \ref{fig:circlefits2}.

<<circlefits2, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Circle fit for each cross section of bullet 2, with part 2 of bullet 1 overlayed.', fig.pos='H'>>=
qplot(y, resid, data=subset(db2, x <= 80 & x >=75), colour=factor(x), geom="line", size=I(1)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group =x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x <= 80, x >=75)[,c("y", "resid", "x")]) + ggtitle("Part 2 of Bullet 1 in black")
@
